---
title: "week4_assignment"
author: "uzma"
date: "21 November 2018"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## The Swiss Dataset

The Swiss dataset contains data about each of the 47 French-speaking provinces of Switzerland in 1888. The following data is collected:

- Fertility,a standardized fertility measure.
- Agriculture,% of males involved in agriculture as occupation.
- Examination,% draftees receiving highest mark on army examination.
- Education,draftees receiving education beyond primary school.
- Catholic,% catholic
- Infant.Mortality,% live births who live less than 1 year.
- Except for Fertility, all variables are measured as a percentage of the population.

## Swiss Dtaset

```{r swiss, echo = TRUE}
head(swiss)
```

## Summary of data

```{r summary, echo = TRUE}
summary(swiss)
```

## Slide with Plot

This app predicts the Fertility, by using two parameters;
- one is % of people receiving education beyond primary school.
here is plot between Fertility and educated people;

```{r plot1}
plot(swiss$Education,swiss$Fertility,xlab = 'educated population',ylab = 'Fertility',bty='n',pch=16,col='blue')
```

## Slide with Plot

- the other predicting parametr is number of people involved in Agriculture accupation.
here is plot between Fertility and Agriculture;

```{r plot2}

plot(swiss$Agriculture,swiss$Fertility,xlab = '% involved in Agriculture',ylab = 'Fertility',bty='n',pch=16,col='blue')
```

## Slide with App Link
we made 2 regression models;

- one compares Fertility and Education,

- other compares Fertility and Agriculture


https://uzmamahmood.shinyapps.io/swissDataApp/



